Exploring the composition of lithic assemblages in Mesolithic south-eastern Norway

### 2021-03-30 analysis/paper/paper.Rmd
Adding some text and references from the analysis proposal to the workshop to test the Zotero functionality in Rmd

# Plots

>>>>

# Introduction

Previous studies of lithic artefacts in Norway have typically had a focus on chronological trends associated with formal tool types [@reitan2016], involved refit-studies of the entirety of individual assemblages [@skar1986], or in-depth analyses concerned with technological processes associated with certain sub-categories of the site inventories -- for example as related to the production of blades [@damlien2016]. Some studies have attempted more comprehensive evaluations of a number of lithic inventories to get at potential site types [@viken2018; @breivik2020], but these have been conducted without support from quantitative frameworks that can help structure such analyses. In sum, previous studies are typically either limited to a small number of sites, to a subset of the inventories, or to narratively and subjectively driven methods. My analysis would aim to employ multivariate exploratory statistics using the entirety of the lithic assemblages associated with a larger number of sites. This would be done to identify latent patterns and structure in the relationship between these, with the ultimate aim of identifying behaviourally induced variation in their composition across time and space. However, the composition of the assemblages can be expected to be determined by a multitude of factors [e.g. @dibble2017], ranging from the impact of natural formation processes to various and intermixed behavioural aspects such as purpose, duration, frequency, and group sizes at visits to the sites. Furthermore, the assemblages are also likely to be impacted by variation in lithic technology, artefact function, use-life and discard patterns, as well as access to raw materials. Finally, analytical and methodological dimensions relating to survey, excavation and classification practices will also influence how the assemblages are defined. Consequently, the proposed analysis would be conducted from an exploratory perspective, where all of these factors should be seen as potential contributors to any observed pattern. In this light, the following sections will present the data to be analysed, a few potential sources of bias that might affect the comparisons to be conducted, while also highlighting a few ways in which idiosyncrasies in the chosen material might alleviate some of these issues.
